Post-Disturbance Tree Community Trajectories in a Neotropical Forest

### 2019-03-26 WholePlotTrajectories.Rmd
abstract

---
title: "Post-Disturbance Tree Community Trajectories in a Neotropical Forest"
author:
  - name: Ariane MIRABEL
    authsuperscript: 1*
  - name: Bruno Herault
    authsuperscript: 2
  - name: Eric Marcon
    authsuperscript: 1
affiliation:
  - affsuperscript: 1
    dptuniv: UMR EcoFoG, AgroParistech, CNRS, Cirad, INRA, Université des Antilles, Université de Guyane.
    address: >
      Campus Agronomique,
      97310 Kourou,
      France.
  - affsuperscript: 2
    dptuniv: INPHB, Institut National Polytechnique Félix Houphoüet-Boigny
    address: >
      Yamoussoukro,
      Ivory Coast.
corrauthor:
    email: ariane.mirabel@ecofog.gf
    url: https://github.com/ArianeMirabel
abstract: 
 Understanding biodiversity trajectories of tropical forests following disturbance and clarifying the link between biodiversity and disturbance is urgent to anticipate the impact of the global change context.
 This calls to highlight the taxonomic and functional facets of tree community trajectories and the underlying processes, and to clarify the link between biodiversity and disturbance, specifically the scope of the Intermediate Disturbance Hypothesis (IDH) that is debated in tropical forests.
 In this study, we analyzed the tree community response to a disturbance gradient in a Neotropical forest through diversity, composition and redundancy post-disturbance trajectories over 30 years. We considered taxonomic trajectories and functional trajectories based on 7 leaf, stem and life-history traits. While taxonomic trajectories differed among communities, functional trajectories remained similar and convergent, and this decoupling was explained by the variations in community functional redundancy mitigating the functional impact of disturbance. We validated the IDH, based on an intensity threshold of 20-25% of AGB removed, and we clarified its scope, showing that it applied to taxonomic but not functional diversity, and applied around 20 years after disturbance when the recruitment of pioneers and late-successionals were balanced. 
 Although consistent, the recovery of community composition, diversity and redundancy remained unachieved after 30 years. This acknowledged the need of decades-long cycles without disturbance to ensure a complete recovery, and questioned tropical forest community resilience after repeated disturbances.
keywords: [Community Ecology, Disturbance Trajectories, Intermediate Disturbance Hypothesis, Mid-term Resilience, Neotropical Forests, Taxonomic and Functional Biodiversity]
preamble: >
  \usepackage{textcomp}
  \DeclareUnicodeCharacter{B0}{\textdegree}
  \usepackage{tabu}
  \usepackage{caption}
  \captionsetup{justification = justified}
  \renewenvironment{table}{\begin{table*}}{\end{table*}\ignorespacesafterend}
  \hyphenation{bio-di-ver-si-ty sap-lings re-or-gan-i-za-tion post-dis-tur-bance dis-tur-bance}
bibliography: references.bib
lang: english
keywordlabel: Keywords
corrauthorlabel: Corresponding author
output:
  bookdown::pdf_book:
    base_format: EcoFoG::article
    keep_tex: TRUE
  bookdown::word_document2: default
  bookdown::gitbook: default
---

>>>>

---
title: "Post-Disturbance Tree Community Trajectories in a Neotropical Forest"
author:
  - name: Ariane MIRABEL
    authsuperscript: 1*
  - name: Bruno Herault
    authsuperscript: 2
  - name: Eric Marcon
    authsuperscript: 1
affiliation:
  - affsuperscript: 1
    dptuniv: UMR EcoFoG, AgroParistech, CNRS, Cirad, INRA, Université des Antilles, Université de Guyane.
    address: >
      Campus Agronomique,
      97310 Kourou,
      France.
  - affsuperscript: 2
    dptuniv: INPHB, Institut National Polytechnique Félix Houphoüet-Boigny
    address: >
      Yamoussoukro,
      Ivory Coast.
corrauthor:
    email: ariane.mirabel@ecofog.gf
    url: https://github.com/ArianeMirabel
abstract: 
 Anticipate the impact of the global change context on tropical forests is now urgent.
 This calls to highlight the taxonomic and functional facets of tree community post-disturbance trajectories and the underlying processes. 
 It also calls to clarify the link between biodiversity and disturbance, specifically the scope of the Intermediate Disturbance Hypothesis (IDH) that is debated in tropical forests.
 In this study, we analyzed the tree community trajectories following a disturbance gradient in a Neotropical forest over 30 years. 
 We considered community taxonomic and functional diversity, composition and redundancy trajectories. We based on the annual botanical inventories of 75 ha of a Neotropical forest and on large trait datasets comprising 7 leaf, stem and life-history traits. 
 We highlighted a decoupling between taxonomic trajectories, that differed among communities, and functional trajectories, remained similar and convergent. We explained this decoupling by the variations in community functional redundancy that mitigated the functional impact of disturbance. Post-disturbance trajectories clarified the scope of the Intermediate Disturbance Hypothesis that was validated regarding taxonomic diversity, with an intensity threshold of 20-25%, but not regarding functional diversity.The IDH applied around 20 years after disturbance when the recruitment of pioneers and late-successionals were balanced. 
 Although consistent, the recovery of community composition, diversity and redundancy remained unachieved after 30 years. This acknowledged the need of decades-long cycles without disturbance to ensure a complete recovery, and questioned tropical forest community resilience after repeated disturbances.
keywords: [Community Ecology, Disturbance Trajectories, Intermediate Disturbance Hypothesis, Mid-term Resilience, Neotropical Forests, Taxonomic and Functional Biodiversity]
preamble: >
  \usepackage{textcomp}
  \DeclareUnicodeCharacter{B0}{\textdegree}
  \usepackage{tabu}
  \usepackage{caption}
  \captionsetup{justification = justified}
  \renewenvironment{table}{\begin{table*}}{\end{table*}\ignorespacesafterend}
  \hyphenation{bio-di-ver-si-ty sap-lings re-or-gan-i-za-tion post-dis-tur-bance dis-tur-bance}
bibliography: references.bib
lang: english
keywordlabel: Keywords
corrauthorlabel: Corresponding author
output:
  bookdown::pdf_book:
    base_format: EcoFoG::article
    keep_tex: TRUE
  bookdown::word_document2: default
  bookdown::gitbook: default
---

### 2019-03-26 WholePlotTrajectories.tex
abstract

\Abstract{
Understanding biodiversity trajectories of tropical forests following
disturbance and clarifying the link between biodiversity and disturbance
is urgent to anticipate the impact of the global change context. This
calls to highlight the taxonomic and functional facets of tree community
trajectories and the underlying processes, and to clarify the link
between biodiversity and disturbance, specifically the scope of the
Intermediate Disturbance Hypothesis (IDH) that is debated in tropical
forests. In this study, we analyzed the tree community response to a
disturbance gradient in a Neotropical forest through diversity,
composition and redundancy post-disturbance trajectories over 30 years.
We considered taxonomic trajectories and functional trajectories based
on 7 leaf, stem and life-history traits. While taxonomic trajectories
differed among communities, functional trajectories remained similar and
convergent, and this decoupling was explained by the variations in
community functional redundancy mitigating the functional impact of
disturbance. We validated the IDH, based on an intensity threshold of
20-25\% of AGB removed, and we clarified its scope, showing that it
applied to taxonomic but not functional diversity, and applied around 20
years after disturbance when the recruitment of pioneers and
late-successionals were balanced. Although consistent, the recovery of
community composition, diversity and redundancy remained unachieved
after 30 years. This acknowledged the need of decades-long cycles
without disturbance to ensure a complete recovery, and questioned
tropical forest community resilience after repeated disturbances.
}

>>>>

\Abstract{
Anticipate the impact of the global change context on tropical forests
is now urgent. This calls to highlight the taxonomic and functional
facets of tree community post-disturbance trajectories and the
underlying processes. It also calls to clarify the link between
biodiversity and disturbance, specifically the scope of the Intermediate
Disturbance Hypothesis (IDH) that is debated in tropical forests. In
this study, we analyzed the tree community trajectories following a
disturbance gradient in a Neotropical forest over 30 years. We
considered community taxonomic and functional diversity, composition and
redundancy trajectories. We based on the annual botanical inventories of
75 ha of a Neotropical forest and on large trait datasets comprising 7
leaf, stem and life-history traits. We highlighted a decoupling between
taxonomic trajectories, that differed among communities, and functional
trajectories, remained similar and convergent. We explained this
decoupling by the variations in community functional redundancy that
mitigated the functional impact of disturbance. Post-disturbance
trajectories clarified the scope of the Intermediate Disturbance
Hypothesis that was validated regarding taxonomic diversity, with an
intensity threshold of 20-25\%, but not regarding functional
diversity.The IDH applied around 20 years after disturbance when the
recruitment of pioneers and late-successionals were balanced. Although
consistent, the recovery of community composition, diversity and
redundancy remained unachieved after 30 years. This acknowledged the
need of decades-long cycles without disturbance to ensure a complete
recovery, and questioned tropical forest community resilience after
repeated disturbances.
}
